Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-17 TACAS2018/paper.tex
sec 6.3 on safety

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Safety of a digitally observed system}\label{sec:cof_safety}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\todo{FWL effects here? they are implicit from equation \ref{eq:observer_LTI_FWL_cf}}

%% Now that we have established convergence, we may examine the safety
%% specification of the state space.
A safety specification gives raise to a requirement on the
states of the model, such that the controller and the observer (namely the 
matrices~$K$ and~$L$) must ensure that the state never violates the
requirement.

In~this work, the safety property is expressed as:
%
\begin{align}
\phi_\mathit{safety}\equiv& \underline{y} \leq y_k \leq \overline{y}
\iff \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
\label{eq:safetyspec}
\end{align}
%
where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
%
%% \begin{align}
%% \phi_\mathit{safety}\equiv& \underline{y} \leq y_k \leq \overline{y}
%% \iff \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
%% \label{eq:safetyspec}
%% \end{align}
%
%% For an observed system, the safety specification is
%% given by a constraint on the output which are considered
%% safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in
%% [\underline{y}\ \ \overline{y}]$)
%% Whilst there are other properties we may
%% include in the verification, we will solely focus on these for simplicity of
%% the explanation.  We assume that we do not want saturation in our
%% system, hence the control loop has only one mode.
%% First we must
%% translate the safety specification into the statespace.  Replacing on the
%% second part of equation \eqref{eq:observer_LTI_cf} we obtain
%% %
%% \begin{equation}
%% \phi_{safety} := \underline{y}<\mat{C}\vec{x}_k<\overline{y}, \forall k \geq 0
%% \label{eq:of_bounds}
%% \end{equation}
%
%% We are not limited to the synthesis of digital stabilizing controllers -- a
%% well known task in the literature on digital control systems -- but target
%% safety requirements with an overall approach that is sound and automated. 
%% More specifically, we require that the closed-loop system meets given safety
%% specifications.  A safety specification gives raise to a requirement on the
%% states of the model, such that the feedback controller (namely the choice of
%% the gains matrix~$K$) must ensure that the state never violates the
%% requirement.  Note that a stable, closed-loop system is not necessarily a
%% safe system: indeed, the state values may leave the safe part of the state
%% space while they converge to the equilibrium, which is typical in the case
%% of oscillatory dynamics.  In~this work, the safety property is expressed as:
%% %
%% \begin{align}
%% \phi_\mathit{safety}\equiv& \underline{y} \leq y_k \leq \overline{y}
%% \iff \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
%% \label{eq:safetyspec}
%% \end{align}

@@

Furthermore, we also need to consider the 
constraints 
\begin{align}
\phi_\mathit{input}\equiv \underline{u} \leq u_k \leq \overline{u}
\label{eq:inputspec}
\end{align}
which comes from physical restrictions in the energy of the system, and
\begin{align}
\phi_\mathit{init}\equiv \mat{G}' \vec{x}_0 \leq \vec{h}'
\label{eq:initspec}
\end{align}

>>>>

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Safety of a digitally observed system}\label{sec:cof_safety}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%% Now that we have established convergence, we may examine the safety
%% specification of the state space.
A safety specification gives raise to a requirement on the
states of the model, such that the controller
must ensure that the state never violates the
requirement.
In~this work, the safety property is expressed as:
%
\begin{align}
  \phi_\mathit{safety}\equiv& \underline{y} \leq y_k \leq \overline{y}
\iff \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
\label{eq:safetyspec}
\end{align}
%
where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
%
Note that FWL effects are not explicitly captured here
as they are implicit from equation \ref{eq:observer_LTI_FWL_cf}.
%
%% \begin{align}
%% \phi_\mathit{safety}\equiv& \underline{y} \leq y_k \leq \overline{y}
%% \iff \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
%% \label{eq:safetyspec}
%% \end{align}
%
%% For an observed system, the safety specification is
%% given by a constraint on the output which are considered
%% safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in
%% [\underline{y}\ \ \overline{y}]$)
%% Whilst there are other properties we may
%% include in the verification, we will solely focus on these for simplicity of
%% the explanation.  We assume that we do not want saturation in our
%% system, hence the control loop has only one mode.
%% First we must
%% translate the safety specification into the statespace.  Replacing on the
%% second part of equation \eqref{eq:observer_LTI_cf} we obtain
%% %
%% \begin{equation}
%% \phi_{safety} := \underline{y}<\mat{C}\vec{x}_k<\overline{y}, \forall k \geq 0
%% \label{eq:of_bounds}
%% \end{equation}
%
%% We are not limited to the synthesis of digital stabilizing controllers -- a
%% well known task in the literature on digital control systems -- but target
%% safety requirements with an overall approach that is sound and automated. 
%% More specifically, we require that the closed-loop system meets given safety
%% specifications.  A safety specification gives raise to a requirement on the
%% states of the model, such that the feedback controller (namely the choice of
%% the gains matrix~$K$) must ensure that the state never violates the
%% requirement.  Note that a stable, closed-loop system is not necessarily a
%% safe system: indeed, the state values may leave the safe part of the state
%% space while they converge to the equilibrium, which is typical in the case
%% of oscillatory dynamics.  In~this work, the safety property is expressed as:
%% %
%% \begin{align}
%% \phi_\mathit{safety}\equiv& \underline{y} \leq y_k \leq \overline{y}
%% \iff \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
%% \label{eq:safetyspec}
%% \end{align}

@@

Furthermore, it is practically relevant to consider the 
constraints $\phi_\mathit{input}$ on the input
signal $u_{k}$ and $\phi_\mathit{init}$ on the initial states $x_0$,
which we assume have given bounds:
%\begin{align}
$\phi_\mathit{input}\equiv \underline{u} \leq u_k \leq \overline{u}$
%\label{eq:inputspec}
%\end{align}
which comes from physical restrictions in the energy of the system, and
%\begin{align}
$\phi_\mathit{init}\equiv \mat{G}' \vec{x}_0 \leq \vec{h}'$,
where $\mat{G}'$ and $\vec{h}'$ describe the initial state-space.
%\label{eq:initspec}
%\end{align}
